Universal Anonymous Signatures

### 2022-10-05 prism-backend/research/gsac/app-building-blocks.tex
Typos and notation fixed. Some important updates pending...

\begin{description}
\item[$\Eparm \gets \ESetup(\Esecpar)$.] Produces public parameters \Eparm given
  a security parameter \Esecpar.
\item[$(\Eek,\Edk) \gets \EKeyGen(\Eparm)$.] Given public parameters \Eparm,
  produces an encryption-decryption key pair $(\Eek,\Edk)$.
\item[$\Ec \gets \EEnc(\Eek,\msg)$.] Encrypts message \msg with encryption key
  \Eek, producing ciphertext \Ec.
\item[$\msg \gets \EDec(\Edk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
  \Edk.
\end{description}

A public-key encryption scheme is correct if, given a honestly generated key
pair $(\Eek,\Edk)$, produced with honestly generated parameters \Eparm,
$\Pr[\EDec(\Edk,\EEnc(\Eek,\msg))=\msg] = 1$ with overwhelming probability.

A public-key encryption scheme has IND-CCA2 security if
$\Pr[\ExpINDCCAiio(\Esecpar) = 1] - \Pr[\ExpINDCCAiiz(\Esecpar) = 1]|$ is
a negligible function of \Esecpar, for any p.p.t. adversary \adv, where
\ExpINDCCAiib is as defined in \figref{fig:indcca2-game}.

\begin{figure}[ht!]
  \scalebox{0.9}{  
    \begin{minipage}[t]{\textwidth}
      \centering      
      \procedure{$\ExpINDCCAiib(\Esecpar)$}{%
        \Eparm \gets \ESetup(\Esecpar) \\
        (\Eek,\Edk) \gets \EKeyGen(\Eparm) \\
        b^* \gets \adv^{\ELR(b,\cdot,\cdot),\EDEC(\Edk,\cdot)}(\Eek),
        ~\textrm{where:} \\
        \pcind \ELR(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\Eek,\msg_b),
        ~\textrm{and} \\
        \pcind \EDEC(\Edk,\Ec)~\textrm{returns}~\EDec(\Edk,\Ec) \\
        \pcif \EDEC~\textrm{has been called with an output of \ELR, abort} \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \label{fig:indcca2-game}
  \caption{IND-CCA2 Game.}
\end{figure}

@@

Although we don't expose commitments directly in our \UAS scheme or
constructions, they are an essential part of \SBCM schemes. Thus, we overview
them briefly next. In a nutshell, a commitment scheme is defined by the
following algorithms:

\begin{description}
\item[$\Cparm \gets \CSetup(\Csecpar)$.] Given a security parameter \Csecpar,
  returns the public parameters \Cparm to commit messages.
\item[$\Ccom \gets \CCommit(\Cparm,\msg;r)$.] Given the public parameters and
  a message \msg, outputs a commitment \Ccom to \msg, for which randomness $r$
  from some predefined randomness space $\mathcal{R}$ is used.
\end{description}

@@

\begin{description}
\item[Binding.] Intuitively, the binding property of commitment schemes means
  that no adversary can change the message that has been committed to. More
  formally, $\Pr[\ExpComBind(\Csecpar) = 1]$ must be a negligible function of
  the security parameter.
\item[Hiding.] The hiding property captures that no adversary should be able to
  learn the message that was committed, when given only the commitment. This is
  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb(\Csecpar)=1|
  b=1] - \Pr[\ExpComHideb(\Csecpar)=1|b=0]|$ must be a negligible function of
  the security parameter.
\end{description}

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpComBind(\Csecpar)$}{%
        \Cparm \gets \CSetup(\Csecpar) \\
        (\msg_0,r_0,\msg_1,r_1) \gets \adv(\Cparm) \\
        \Ccom_0 \gets \CCommit(\Cparm,\msg_0,r_0) \\
        \Ccom_1 \gets \CCommit(\Cparm,\msg_1,r_1) \\
        \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpComHideb(\secpar)$}{%
        \Cparm \gets \CSetup(\secpar) \\
        b' \gets \adv^{COM(\Cparm,\cdot,\cdot)},~\textrm{where}: \\
        \pcind COM(\Cparm,\msg_0,\msg_1): \\
        \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\Cparm,\msg_b,r) \\
        % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
        % r \getr \mathcal{R} \\
        % \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
        % b' \gets \adv(st,\Ccom) \\
        \pcreturn b'
      }
    \end{minipage}
  }
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

\paragraph{Commitments on Blocks of Messages.} We also use an extension
of commitment schemes that allows committing to multiple messages at once. The
properties we need are the same, and their definitions are extended in the
natural way. Namely, $\CCommit$ receives a vector/block of messages, \msgset
instead of a single message. In the games, the adversary returns sets of
messages and, in the binding game, the comparison $\msg_0 \neq \msg_1$ now
compares sets $\msgset_0$ and $\msgset_1$, which must differ in at least one
element. This extension is straight-forward, for instance, from Pedersen
commitments \cite{bcc+15}.

\subsection{Simulation-Extractable Non-Interactive Zero-Knowledge
  Proofs of Knowledge}
\label{sapp:nizk}

@@

\begin{description}
\item[$\NIZKcrs \gets \NIZKSetup(\NIZKsecpar)$.] Generates a CRS \NIZKcrs from
  security parameters \NIZKsecpar.
\item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.] Given \NIZKcrs,
  statement \NIZKx, and witness \NIZKw, creates a proof \NIZKproof.
\item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.] Checks whether
  \NIZKproof is a valid proof for \NIZKx.
\end{description}

Any zero-knowledge proof of knowledge must meet completeness, soundness and
zero-knowledge,properties. We further need an extra property, called
\emph{simulation-extractability} \cite{cl06}, which amplifies the security
requirements of (simulation-) soundness.
%
To define more formally the properties we need, we have to define three extra
algorithms:

\begin{description}
\item[$(\NIZKcrs,\NIZKtrap) \gets \NIZKSimSetup(\NIZKsecpar)$.] Produces a
  \NIZKcrs as the \NIZKSetup algorithm, along with a trapdoor \NIZKtrap.
\item[$\NIZKproof \gets \NIZKSim(\NIZKcrs,\NIZKtrap,\NIZKx)$.] Given a trapdoor
  \NIZKtrap produced by \NIZKSimSetup, and a statement $\NIZKx \in \NIZKLang$,
  produces a simulated proof \NIZKproof of $\NIZKx \in \NIZKLang$.
\item[$\NIZKw \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof)$.] Given
  a trapdoor \NIZKtrap produced by \NIZKSimSetup, and a proof \NIZKproof for
  $\NIZKx \in \NIZKLang$, returns a valid \NIZKw for \NIZKx.
\end{description}

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and super-index when
clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,\SimSetup,
\Sim,\Extract)$ needs to meet the following properties:

\paragraph{Completeness.} %
Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel$, any honest prover will be
able to create a proof \NIZKproof that is accepted by any honest verifier, with
overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp(\NIZKsecpar)
\rbrack = 1$ with overwhelming probability, for any p.p.t. \adv, for
\ExpNIZKComp in \figref{fig:nizk-games}.

\paragraph{Soundness.} %
Ensures that no adversary can create proofs accepted by \Verify, for
statements $\NIZKx \notin \NIZKLang$, except with negligible probability. That
is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound
(\NIZKsecpar)\rbrack=1$ with overwhelming probability. If this holds only
against p.p.t. adversaries, we talk of Non-Interactive \emph{arguments}, while
if soundness holds even against unbounded adversaries, we talks about
Non-Interactive proofs.

\paragraph{Zero-knowledge.} %
Intuitively, captures that no information can be learned from a statement and
proof pair, beyond their validity (or not). This is captured by requiring the
adversary to distinguish between a run in the real world ($b=0$), where the
setup is done with \Setup, and $\adv$ has access to an honest prover
\Prove; and a run in an ideal world ($b=1$), where the setup is replaced by
\SimSetup, and proofs are simulated with the help of the trapdoor produced by
\SimSetup, except when $\adv$ specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$. Note
that, in the context of simulation-extractable NIZK, this property not only
requires that the simulated proofs are indistinguishable to the real ones; it
also requires that \SimSetup is indistinguishable from \Setup. All this is
formalised by requiring that $|\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 1] -
\Pr[\ExpNIZKZKb(\NIZKsecpar) = 1 | b = 0]$ be a negligible function of \secpar,
where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.

\paragraph{Simulation-Extractability.} As stated, simulation-extractability
is an extension to simulation soundness. In a nutshell,
simulation-extractability requires that, even after having received a polynomial
number of simulated proofs of knowledge, no adversary can output a valid proof
of knowledge from which no witness can be extracted. It implies simulation
soundness, which ``just'' requires that no adversary can produce a valid proof
after having seen polynomially many simulated proofs (but does not guarantee
extraction). Formally, for simulation-extractability we require that
$\Pr[\ExpNIZKSimExt(\NIZKsecpar)] = 1$ is a negligible function of \secpar,
where \ExpNIZKSimExt is defined in \figref{fig:nizk-games}.

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
        \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
        \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
        \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
        b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
        \pcreturn b \\
      }
      \procedure{$\ExpNIZKSimExt(\NIZKsecpar)$}{%
        (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\NIZKsecpar) \\
        (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
        (\NIZKcrs) \\
        \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
        \pcind \pcind
        \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
        \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
        \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
        \pcif \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
        (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
        \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}: \\
        \pcind \pcreturn 1 \\
        \pcreturn 0
      }    
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
        \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
        \pcif \NIZKx \notin \NIZKLang \land
        \Verify(\NIZKcrs,\NIZKproof,\NIZKx): \\
        \pcind \pcreturn 0 \\
        \pcreturn 1 \\
      }

      \procedure{$\ExpNIZKZKb(\NIZKsecpar)$}{%
        \pcif b = 0: \\
        \pcind \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
        \pcif b = 1: \\
        \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
        \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
        \textrm{where} \\
        \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
        \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
        \in \NIZKRel \\
        \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
      }    
    \end{minipage}
  }
  \label{fig:nizk-games}
  \caption{Games for Simulation-Extractable NIZK schemes.}
\end{figure}

As studied in \cite{cl06}, simulation-extractable NIZKPoKs formalise the concept
of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
that, given an $(\NIZKx,\NIZKw)$ pair from an NP relation, we can treat \NIZKx
as a public key, and \NIZKw as its corresponding private key, and leverage them
to build digital signature schemes -- with the advantage of being able to do so
while proving arbitrary claims, as long as they can be represented as an NP
relation. We note that, given a simulation-extractable NIZK system, it is
straightforward to build a signature of knowledge by adding the message to be
signed in the statement of the NIZK.

@@

\paragraph{Correctness.} %
Informally, an \SBM scheme is correct if signatures generated between an honest
party running running \SBMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\smsg \cup \overline{\smsg}$ that is
accepted by \SBMVerify.

@@

For our generic constructions, we use interactive signing protocols between a
user and a signer, where the user has a block of messages to sign blindly, and
both receive a common block of messages to be also included in the resulting
signature. This is precisely the case of partially blind signatures, that
collapse to blind signatures when there is no common message between user
and signer; and to conventional signatures when the user does not input a
message to be blindly signed \cite{ao00}. Partially blind signatures, as
blind signatures \cite{ps96}, cannot be modelled with the conventional security
against existential forgeries. Simply because the user is actually expected to
be able to create signatures on messages unknown to the signer, which formally
translates into the impossibility to check whether a signature output by the
adversary is over a message that has been queried to the signing oracle or not.
Thus, instead of using the conventional existential unforgeability property,
(partially) blind signature schemes move to the ``one-more'' paradigm, which
demands that no adversary can produce $n+1$ distinct signatures after having
interacted with the signing oracle at most $n$ times.

@@

\begin{description}
\item[$\SBCMparm \gets \SBCMSetup(\SBCMsecpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\SBCMvk,\SBCMsk) \gets \SBCMKeyGen(\SBCMparm)$.] Generates a
  verification-signing key pair.
\item[$(\SBCMcom,\pi,r) \gets \SBCMBlind(\SBCMvk,\osmsg,\smsg)$.] A user
  computes commitment \SBCMcom to request a signature over messages \osmsg (in
  committed form) and \smsg (in plain form), to signer with verification key
  \SBCMvk. The output is the commitment \SBCMcom, the randomness $r$ used to
  compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
  \SBCMcom.
\item[$\SBCMbsig \gets \SBCMSign(\SBCMsk,\SBCMcom,\pi,\smsg)$.] The
  signer, with signing key \SBCMsk, produces a blind signature \SBCMbsig over
  the messages committed to in commitment \SBCMcom, as well as the messages in
  \smsg, with associated proof $\pi$.
\item[$\SBCMsig \gets \SBCMUnblind(\SBCMvk,\SBCMbsig,\SBCMcom,r,\osmsg,\smsg)$.]
  A user, who requested a signature over \osmsg and \smsg, where \SBCMcom is a
  commitment over \osmsg using randomness $r$, finalises the signature,
  computing \SBCMsig from the signer's partial signature \SBCMbsig.
\item[$1/0 \gets \SBCMVerify(\SBCMvk,\SBCMsig,\osmsg,\smsg)$.] Checks
  whether \SBCMsig is a valid signature over the set of messages \osmsg and
  \smsg, under verification key \SBCMvk.
\end{description}

The correctness and security properties are then defined as follows.

>>>>

\begin{description}
\item[$\parm \gets \ESetup(\secpar)$.] Produces public parameters \parm given
  a security parameter \secpar.
\item[$(\ek,\dk) \gets \EKeyGen(\parm)$.] Given public parameters \parm,
  produces an encryption-decryption key pair $(\ek,\dk)$.
\item[$\Ec \gets \EEnc(\ek,\msg)$.] Encrypts message \msg with encryption key
  \ek, producing ciphertext \c.
\item[$\msg \gets \EDec(\dk,\Ec)$.] Decrypts ciphertext \Ec with decryption key
  \dk.
\end{description}

A public-key encryption scheme is correct if, given a honestly generated key
pair $(\ek,\dk)$, produced with honestly generated parameters \Eparm,
$\Pr[\EDec(\dk,\EEnc(\ek,\msg))=\msg] = 1$ with overwhelming probability.

A public-key encryption scheme has IND-CCA2 security if
$\Pr[\ExpINDCCAiio(\secpar) = 1] - \Pr[\ExpINDCCAiiz(\secpar) = 1]|$ is
a negligible function of \Esecpar, for any p.p.t. adversary \adv, where
\ExpINDCCAiib is as defined in \figref{fig:indcca2-game}.

\begin{figure}[ht!]
  \scalebox{0.9}{  
    \begin{minipage}[t]{\textwidth}
      \centering      
      \procedure{$\ExpINDCCAiib(\secpar)$}{%
        \parm \gets \ESetup(\secpar) \\
        (\ek,\dk) \gets \EKeyGen(\parm) \\
        b^* \gets \adv^{\oracle{\ELR}(b,\cdot,\cdot),
          \oracle{\EDEC}(\dk,\cdot)}(\ek),
        ~\textrm{where:} \\
        \pcind \oracle{\ELR}(b,\msg_0,\msg_1)~\textrm{returns}~\EEnc(\ek,\msg_b),
        ~\textrm{and} \\
        \pcind \oracle{\EDEC}(\dk,\Ec)~\textrm{returns}~\EDec(\dk,\Ec) \\
        \pcif \oracle{\EDEC}~\textrm{has been called with an output of \ELR,
          abort} \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \label{fig:indcca2-game}
  \caption{IND-CCA2 Game.}
\end{figure}

@@

Although we don't directly leverage commitments fucntionality in our \UAS scheme
or constructions, they are an essential part of \SBCM schemes, which we present
in a following section. Thus, we overview commitment schemes briefly now. In a
nutshell, a commitment scheme is defined by the following algorithms:

\begin{description}
\item[$\parm \gets \CSetup(\secpar)$.] Given a security parameter \secpar,
  returns the public parameters \parm to commit messages.
\item[$\Ccom \gets \CCommit(\parm,\msg;r)$.] Given the public parameters and
  a message \msg, outputs a commitment \com to \msg, for which randomness $r$
  from some predefined randomness space $\mathcal{R}$ is used.
\end{description}

@@

\begin{description}
\item[Binding.] Intuitively, the binding property of commitment schemes means
  that no adversary can change the message that has been committed to. More
  formally, $\Pr[\ExpComBind(\secpar) = 1]$ must be a negligible function of
  the security parameter.
\item[Hiding.] The hiding property captures that no adversary should be able to
  learn the message that was committed, when given only the commitment. This is
  formally defined through \ExpComHideb, where $|\Pr[\ExpComHideb(\secpar)=1|
  b=1] - \Pr[\ExpComHideb(\secpar)=1|b=0]|$ must be a negligible function of
  the security parameter.
\end{description}

\begin{figure}[ht!]
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpComBind(\secpar)$}{%
        \parm \gets \CSetup(\secpar) \\
        (\msg_0,r_0,\msg_1,r_1) \gets \adv(\parm) \\
        \Ccom_0 \gets \CCommit(\parm,\msg_0,r_0) \\
        \Ccom_1 \gets \CCommit(\parm,\msg_1,r_1) \\
        \pcif \msg_0 \neq \msg_1 \land \Ccom_0 = \Ccom_1: \pcreturn 1 \\
        \pcreturn 0
      }
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
      \procedure{$\ExpComHideb(\secpar)$}{%
        \parm \gets \CSetup(\secpar) \\
        b' \gets \adv^{\oracle{COM}(\parm,\cdot,\cdot)},~\textrm{where}: \\
        \pcind COM(\parm,\msg_0,\msg_1): \\
        \pcind \pcind r \getr \mathcal{R};~\pcreturn \CCommit(\parm,\msg_b,r) \\
        % (\msg_0,\msg_1,st) \gets \adv(\Cparm) \\
        % r \getr \mathcal{R} \\
        % \Ccom \gets \CCommit(\Cparm,\msg_b,r) \\
        % b' \gets \adv(st,\Ccom) \\
        \pcreturn b'
      }
    \end{minipage}
  }
  \label{fig:com-games}
  \caption{Games for commitment schemes.}
\end{figure}

\paragraph{Commitments on Blocks of Messages.} We also use an extension
of commitment schemes that allows committing to multiple messages at once. The
properties we need are the same, and their definitions are extended in the
natural way. Namely, $\CCommit$ receives a vector/block of messages, \msgset
instead of a single message. In the games, the adversary returns sets of
messages and, in the binding game, the comparison $\msg_0 \neq \msg_1$ now
compares sets $\msgset_0$ and $\msgset_1$, which must differ in at least one
element. This extension is straightforward, for instance, from Pedersen
commitments \cite{bcc+15}.

\subsection{Simulation Extractable Non-Interactive Zero-Knowledge
  Proofs of Knowledge}
\label{sapp:nizk}

@@

\begin{description}
\item[$\NIZKcrs \gets \NIZKSetup(\secpar)$.] Generates a CRS \NIZKcrs from
  security parameters \secpar.
\item[$\NIZKproof \gets \NIZKProve(\NIZKcrs,\NIZKx,\NIZKw)$.] Given \NIZKcrs,
  statement \NIZKx, and witness \NIZKw, creates a proof \NIZKproof.
\item[$1/0 \gets \NIZKVerify(\NIZKcrs,\NIZKproof,\NIZKx)$.] Checks whether
  \NIZKproof is a valid proof for \NIZKx.
\end{description}

Any zero-knowledge proof of knowledge must meet completeness, soundness, and
zero-knowledge properties. We further need an extra property, called
\emph{simulation extractability} \cite{cl06}, which amplifies the security
requirements of (simulation-) soundness.
%
To define more formally the properties we need, we have to define three extra
algorithms:

\begin{description}
\item[$(\NIZKcrs,\NIZKtrap) \gets \NIZKSimSetup(\secpar)$.] Produces a
  \NIZKcrs as the \NIZKSetup algorithm, along with a trapdoor \NIZKtrap.
\item[$\NIZKproof \gets \NIZKSim(\NIZKcrs,\NIZKtrap,\NIZKx)$.] Given a trapdoor
  \NIZKtrap produced by \NIZKSimSetup, and a statement $\NIZKx \in \NIZKLang$,
  produces a simulated proof \NIZKproof of $\NIZKx \in \NIZKLang$.
\item[$\NIZKw \gets \NIZKExtract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof)$.] Given
  a trapdoor \NIZKtrap produced by \NIZKSimSetup, and a proof \NIZKproof for
  $\NIZKx \in \NIZKLang$, returns a valid \NIZKw for \NIZKx.
\end{description}

When we want to make explicit the NP relation \NIZKRel to which the previous
algorithms refer to, we use $\NIZKSetup^\NIZKRel,\NIZKProve^\NIZKRel$, 
$\NIZKVerify^\NIZKRel$, etc., and omit the \NIZK prefix and super-index when
clear from context. Altogether, the tuple $(\Setup,\Prove,\Verify,
\helper{\SimSetup},\helper{\Sim},\helper{\Extract})$ needs to meet the following
properties:

\paragraph{Completeness.} %
Ensures that, for any $(\NIZKx,\NIZKw) \in \NIZKRel$, any honest prover will be
able to create a proof \NIZKproof that is accepted by any honest verifier, with
overwhelming probability. More precisely, $\Pr\lbrack\ExpNIZKComp(\secpar)
\rbrack = 1$ with overwhelming probability, for any p.p.t. \adv, for
\ExpNIZKComp in \figref{fig:nizk-games}.

\paragraph{Soundness.} %
Ensures that no adversary can create proofs accepted by \Verify, for
statements $\NIZKx \notin \NIZKLang$, except with negligible probability. That
is, for \ExpNIZKSound as in \figref{fig:nizk-games}, $\Pr\lbrack\ExpNIZKSound
(\NIZKsecpar)\rbrack=1$ with overwhelming probability. If this holds only
against p.p.t. adversaries, we talk of non-interactive \emph{arguments}, while
if soundness holds even against unbounded adversaries, we talk about
non-interactive proofs.

\paragraph{Zero-knowledge.} %
Intuitively, captures that no information can be learned from a statement and
proof pair, beyond their validity (or not). This is captured by requiring the
adversary to distinguish between a run in the real world ($b=0$), where the
setup is done with \Setup, and $\adv$ has access to an honest prover
\Prove; and a run in an ideal world ($b=1$), where the setup is replaced by
\SimSetup, and proofs are simulated with the help of the trapdoor produced by
\SimSetup, except when $\adv$ specifies $(\NIZKx,\NIZKw) \notin \NIZKRel$. Note
that, in the context of simulation extractable NIZK, this property not only
requires that the simulated proofs are indistinguishable to the real ones; it
also requires that \SimSetup is indistinguishable from \Setup. All this is
formalised by requiring that $|\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 1] -
\Pr[\ExpNIZKZKb(\secpar) = 1 | b = 0]$ be a negligible function of \secpar,
where \ExpNIZKZKb is as defined in \figref{fig:nizk-games}.

\paragraph{Simulation Extractability.} As stated, simulation extractability
is an extension to simulation soundness, which is in turn an extension to
knowledge soundness. In a nutshell,
simulation extractability requires that, even after having received a polynomial
number of simulated proofs of knowledge, no adversary can output a valid proof
of knowledge from which no witness can be extracted. It implies simulation
soundness, which ``just'' requires that no adversary can produce a valid proof
after having seen polynomially many simulated proofs (but does not guarantee
extraction). Formally, for simulation extractability we require that
$\Pr[\ExpNIZKSimExt(\secpar)] = 1$ is a negligible function of \secpar,
where \ExpNIZKSimExt is defined in \figref{fig:nizk-games}.

\begin{figure}[ht!]
  \centering
  \scalebox{0.85}{
    \begin{minipage}[t]{0.55\textwidth}
      \procedure{$\ExpNIZKComp(\NIZKsecpar)$}{%
        \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        (\NIZKx,\NIZKw) \gets \adv(\NIZKcrs) \\
        \pcif (\NIZKx,\NIZKw) \notin \NIZKRel: \pcreturn 0 \\
        \NIZKproof \gets \Prove(\NIZKcrs,\NIZKx,\NIZKw) \\
        b \gets \Verify(\NIZKcrs,\NIZKproof,\NIZKx) \\
        \pcreturn b \\
      }
      \procedure{$\ExpNIZKSimExt(\NIZKsecpar)$}{%
        (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\NIZKsecpar) \\
        (\NIZKx,\NIZKproof) \gets \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}
        (\NIZKcrs) \\
        \pcind \textrm{Where}~\Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
        \pcind \pcind
        \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw) \in \NIZKRel \\
        \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel \\
        \NIZKw' \gets \Extract(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKproof) \\
        \pcreturn \Verify(\NIZKcrs,\NIZKproof,\NIZKx) = 1 \land
        (\NIZKx,\NIZKw') \notin \NIZKRel~\land \\
        \pcind \NIZKx~\textrm{was not queried to $\Sim$ via $\Sim'$}
      }    
    \end{minipage}
    \begin{minipage}[t]{0.55\textwidth}
      \procedure{$\ExpNIZKSound(\NIZKsecpar)$}{%
        \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        (\NIZKproof,\NIZKx) \gets \adv(\NIZKcrs) \\
        \pcreturn 1 - (\NIZKx \notin \NIZKLang \land
        \Verify(\NIZKcrs,\NIZKproof,\NIZKx)) \\
      }

      \procedure{$\ExpNIZKZKb(\NIZKsecpar)$}{%
        \pcif b = 0: \\
        \pcind \NIZKcrs \gets \Setup(\NIZKsecpar) \\
        \pcind \pcreturn \adv^{\Prove(\NIZKcrs,\cdot,\cdot)}(\NIZKcrs) \\
        \pcif b = 1: \\
        \pcind (\NIZKcrs,\NIZKtrap) \gets \SimSetup(\secpar) \\
        \pcind \pcreturn \adv^{\Sim'(\NIZKcrs,\NIZKtrap,\cdot,\cdot)}(\NIZKcrs),~
        \textrm{where} \\
        \pcind \Sim'(\NIZKcrs,\NIZKtrap,\NIZKx,\NIZKw)~\textrm{returns} \\
        \pcind \pcind \Sim(\NIZKcrs,\NIZKtrap,\NIZKx)~\pcif (\NIZKx,\NIZKw)
        \in \NIZKRel \\
        \pcind \pcind \bot~\pcif (\NIZKx,\NIZKw) \notin \NIZKRel
      }    
    \end{minipage}
  }
  \label{fig:nizk-games}
  \caption{Games for Simulation Extractable NIZK schemes.}
\end{figure}

As studied in \cite{cl06}, simulation extractable NIZKPoKs formalise the concept
of ``signatures of knowledge'' (see, e.g., \cite{cs97}). Which basically means
that, given an $(\NIZKx,\NIZKw)$ pair from an NP relation, we can treat \NIZKx
as a public key, and \NIZKw as its corresponding private key, and leverage them
to build digital signature schemes -- with the advantage of being able to do so
while proving arbitrary claims, as long as they can be represented as an NP
relation. We note that, given a simulation extractable NIZK system, it is
straightforward to build a signature of knowledge by adding the message to be
signed in the statement of the NIZK.

@@

\paragraph{Correctness.} %
Informally, an \SBM scheme is correct if signatures generated between an honest
party running running \SBMSign over \smsg, for honestly generated parameters
and key pairs, results in a signature over $\smsg \cup \osmsg$ that is
accepted by \SBMVerify.

@@

For our generic constructions, we use interactive signing protocols between a
user and a signer, where the user has a block of messages to sign blindly, and
both receive a common block of messages to be also included in the resulting
signature. This is precisely the case of partially blind signatures, that
collapse to blind signatures when there is no common message between user
and signer; and to conventional signatures when the user does not input a
message to be blindly signed \cite{ao00}. Partially blind signatures, as
blind signatures \cite{ps96}, don't typically follow the conventional security
against existential forgeries. Simply because the user is actually expected to
be able to create signatures on messages unknown to the signer, which formally
translates into the impossibility to check whether a signature output by the
adversary is over a message that has been queried to the signing oracle or not.
Thus, instead of using the conventional existential unforgeability property,
(partially) blind signature schemes move to the ``one-more'' paradigm, which
demands that no adversary can produce $n+1$ distinct signatures after having
interacted with the signing oracle at most $n$ times.

@@

\begin{description}
\item[$\parm \gets \SBCMSetup(\secpar)$.] It produces public parameters
  for the other algorithms, given an input security parameter \SBCMsecpar.
\item[$(\vk,\SBCMsk) \gets \SBCMKeyGen(\parm)$.] Generates a
  verification-signing key pair.
\item[$(\Ccom,\pi,r) \gets \SBCMBlind(\vk,\osmsg,\smsg)$.] A user
  computes commitment \Ccom to request a signature over messages \osmsg (in
  committed form) and \smsg (in plain form), to signer with verification key
  \vk. The output is the commitment \Ccom, the randomness $r$ used to
  compute it, and a proof $\pi$ proving knowledge of \osmsg and \smsg in
  \Ccom.
\item[$\bsig \gets \SBCMSign(\sk,\Ccom,\pi,\smsg)$.] The
  signer, with signing key \sk, produces a blind signature \bsig over
  the messages committed to in commitment \Ccom, as well as the messages in
  \smsg, with associated proof $\pi$.
\item[$\sig \gets \SBCMUnblind(\vk,\bsig,\Ccom,r,\osmsg,\smsg)$.]
  A user, who requested a signature over \osmsg and \smsg, where \Ccom is a
  commitment over \osmsg using randomness $r$, finalises the signature,
  computing \sig from the signer's partial signature \bsig.
\item[$1/0 \gets \SBCMVerify(\vk,\sig,\osmsg,\smsg)$.] Checks
  whether \sig is a valid signature over the set of messages \osmsg and
  \smsg, under verification key \vk.
\end{description}

The correctness and security properties are defined as follows.
